---
title: "Import data"
author: "Isaac Verminck"
date: "`r Sys.Date()`"
output: pdf_document
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}

library(knitr)

opts_chunk$set(echo=TRUE,
               warning=FALSE,
               message=FALSE,
               cache=FALSE)

devtools::load_all(here::here())

```

# Import data

## Data source

Data on divorces and marriages can be found on the [Statbel site](https://statbel.fgov.be/nl/themas/bevolking/huwelijken-en-echtscheidingen).

For most data we have the same information for marriages and divorces:

* muncipality
* age
* civil state
* nationality
* profession

For marriages we have data from 2013-2016, for divorces 2012-2016. We'll limit ourselves to 2013-2016

Let's focus on age since a lot of interesting questions immediately come to mind:

* at what age do people marry?
* at what age do people divorce?
* what's the age difference between people marrying?

## Download data

```{r download, eval = FALSE}
types <- c("divorce","marriage")
years <- paste0("201", 3:6)

rep_years <- rep(years, times = length(types))
rep_types <- rep(types, each = length(years))

purrr::walk2(.x = rep_years,
             .y = rep_types,
             ~download(year = .x, type = .y))

```



