---
title: "Import data"
author: "Isaac Verminck"
date: "`r Sys.Date()`"
output: pdf_document
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}

library(knitr)

opts_chunk$set(echo=TRUE,
               warning=FALSE,
               message=FALSE,
               cache=FALSE)

devtools::load_all(here::here())

```

# Tidy data

## At what age do people marry?

The first question we want to investigate is at what age people marry. This data is available in the *year_of_birth* tab of the *marriage* files.

We'd like to have a single dataframe indicating for each age how many people marry. However, when loading the data isn't coded in the way we want. 

```{r year_of_birth_issues}

select_worksheet(worksheet = "year_of_birth",
                 year = "2013",
                 type = "divorce")[1:20, ]



```


There are several issues:

* the name of the analysis is repeated as header
* there's a total row at the top
* at the bottom the source of the data is mentioned
* we have the data by year while we want a single dataframe
* regions are separate variables while we want a single variable region with the regions as values
* distinction is made between first and second spouses while we don't care about this distinction
* people with the same ages can be born in two different years
* the year in which the data were gathered isn't mentioned explicitly
* the type of data (divorce or marriage) isn't mentioned explicitly
* variables are coded as character instead of factors (e.g. region)

We create a function to solve each issue, apply these to each dataframe and then bind all dataframes for each year together.
Small note: additional data on gender is provided from 2015 on. Making a modification to incorporate this hasn't been done yet so for the moment the focus is on the data 2013-2014.

```{r tidy_year_of_birth}
types <- c("divorce","marriage")
years <- paste0("201", 3:4)

rep_years <- rep(years, times = length(types))
rep_types <- rep(types, each = length(years))

worksheets <- map2(.x = rep_years,
                   .y = rep_types,
                   .f = ~select_worksheet(worksheet = "year_of_birth",
                                          year = .x,
                                          type = .y)
                   )

tidy_args <- list(worksheet = worksheets,
                  year = rep_years,
                  type = rep_types)
tidy_dfs <- pmap(tidy_args,
                 function(worksheet, year, type) tidy_year_of_birth(worksheet, year, type)
                 )

year_of_birth <- bind_together(tidy_dfs)

save(year_of_birth,
     file = paste(data_path, "year_of_birth.RData", sep = "/")
     ) # data_path is object in tidy-year_of_birth.R

```

